---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette introduces the **SASPACerShiny** package,  
a Shiny-based graphical interface for the SAS package creation.  
It provides a convenient way to create SAS packages without directly editing Excel or configuration files.  

# Installation

You can install the development version from GitHub:

```r
# install.packages("remotes")
remotes::install_github("Nakaya-Ryo/SASPACerShiny")
```

Then load the package:

```{r setup}
library(SASPACerShiny)
```

# Quick Start

The main entry point is the `run_app()` function, which launches the Shiny application:

```{r eval=FALSE}
run_app()
```

This will open the GUI in a new window.  

# Basic Workflow

1. **Prepare SAS package information to create**  
   - Define your SAS package metadata  

2. **Launch the Shiny app**  
   ```r
   SASPACerShiny::run_app()
   ```

3. **Interact with the GUI**  
   - Add tabs for macros, datasets, formats, etc.  
   - Export the source package files/folders as a zip  

# Example: Creating a Minimal SAS Package

```{r eval=FALSE}
# Launch app
run_app()

# In the GUI:
#  - Create new tab if necessary
#  - Add a macro definition
#  - Run and download zip
```

# References

- SASPACer GitHub repository: <https://github.com/Nakaya-Ryo/SASPACer>  
- SASPACerShiny GitHub repository: <https://github.com/Nakaya-Ryo/SASPACerShiny>  
- [Shiny documentation](https://shiny.posit.co/r/)  
- [Writing R vignettes](https://r-pkgs.org/vignettes.html)

